troubleshooting

### 2024-09-19 README.Rmd
major structural changes after Bioconductor feedback

---
output:
  github_document: default
  self_contained: default
---

@@

<!-- badges: start -->
[![R-CMD-check](https://github.com/baynec2/mspms/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/baynec2/mspms/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/baynec2/mspms/branch/main/graph/badge.svg)](https://app.codecov.io/gh/baynec2/mspms?branch=main)
[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/mspms.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/mspms)
<!-- badges: end -->

The goal of mspms is provide a concise code-base for the normalization and 
data processing required to analyze data from the 
[Multiplex Substrate Profiling by Mass Spectrometry (MSP-MS) method](https://pubmed.ncbi.nlm.nih.gov/36948708/).

@@

```{r,eval = FALSE}
mspms::generate_report(
  prepared_data = mspms::peaks_prepared_data,
  design_matrix = mspms::design_matrix,
  outdir = "../Desktop/mspms_report"
)
```

The above command will generate a .html file containing a general mspms analysis.

@@

There are 4 different types of functions in this package.

1. Making mspms generically useful. These functions are focused on making mspms 
more generally useful to a wider audience outside of the very specific workflow
traditionally used in the O’Donoghue lab. Allows for the use of other types of
upstream proteomic data processing, different peptide libraries, etc.

2. Data processing/ normalization. These functions allow the user to normalize
and process the MSP-MS data.

@@

**Making mspms generically useful**.   
1. *prepare_peaks()*:Takes two input files from PEAKS and combines them. 
2. *prepare_pd()*: prepares exported files from proteome discoverer.  
3. *calculate_all_cleavages()*: Calculates all possible cleavages for peptide
library sequences.

**Data Processing/ Normalization**.  
1. *normalyze()*: Normalizes values.     
2. *handle_outliers()*: Looks for outliers across replicates. Removes them.       
3. *impute()*: Imputes data for missing values (not including NAs introduced 
by handle_outliers()).  
4. *join_with_library()*: Joins the normalized data with the peptide library 
sequences.  
5. *add_cleavages()*: Figures out the locations of the detected cleavages within
the library of peptide sequences used. Is it cleaved at the N or C terminus, 
or both? Uses *cterm_cleavage()* and *nterm_cleavage()* to do this.      
6. *polish()*: combines the cleavage info into one column. Discards peptides
that were cleaved on both sides or not at all.  
7. *prepare_for_stats()*: Reshapes the data into a long format and appends the 
data in the design matrix to make statistical testing easy to perform.  
8 *mspms():* combines all of the above functions into one convenient function.

**Calculations/ Statistics**.   
1. *mspms_log2fc()*: Calculates the log2 fold change across experimental 
conditions relative to T0.  
2.*mspms_t_tests()*: Conducts T-tests to determine if there are any peptides 
that are significantly different across experimental conditions relative to time 
0.  
3. *log2fc_t_test()*: Combines results from mspms_log2fc() and mspms_t_tests() 
into one convenient tibble.   
4. *log2fct_condition()*: Calculates the log2 fold change and t tests for the 
specified condition at a user specified time.    
5.*log2fct_time()*: Calculates the log2 fold change and t tests between the 
specified times within a user specified time.   
6. *mspms_anova()*: Conducts ANOVA tests to determine if there are any peptides 
that are significantly different across all time points.   
7. *count_cleavages_per_pos():* Counts the number of cleavages at each position 
of the library. Useful for determining endoprotease vs exoprotease activity.

**Data Visualization**.   
1. *plot_heatmap()*: Conducts hierarchical clustering analysis and plots an
interactive heatmap to visualize overall patterns in the data.    
2. *plot_pca()*: PCA analysis to visualize the data in a 2D space.  
3. *plot_time_course()*: Plot peptides over time by condition.  
4. *plot_cleavages_per_pos()*: Plot the number of cleavages at each position 
in the library.Useful for determining endoprotease vs exoprotease activity.

**Icelogo**.

1. *calc_AA_count_of_motif()*: calculates the count of each amino acid at each
position in a vector of motifs.  
2. *calc_AA_prop_of_motif()*: calculates the proportion of each amino acid at 
each position from the output of calc_AA_count_of_motif().  
3. *calc_AA_motif_zscore()*: calculates z scores for each amino acid at each 
position in a vector of motifs.  
4. *calc_AA_percent_difference()*: calculates the percentage difference of 
5. *prepare_sig_p_dif()*: prepares the data for plotting percent difference 
icelogos. Removes AAs at positions that are not significantly different.  
6. *prepare_fc()*: prepares the data for plotting fold change icelogos.
Removes AAs at positions that are not significantly different.  
7. *plot_pd_icelogo()*: plots a percent difference icelogo.  
8. *plot_fc_icelogo()*: plots a fold change ice logo.  
9. *plot_icelogo()*:  wraps plot_pd_icelogo() and plot_fc_icelogo() into 
one function.  
10. *plot_all_icelogos()*: convenience function to plot all icelogos relative to 
time 0 from an experiment.    
**Reports**. 
1. *generate_report()*: Generates a simple analysis of the mspms data that 
should be generically applicable to all mspms experiments.

## Making Generically Usefull.

### Formating Peaks File Outputs.

All analysis performed by this package is downstream of the data generated by 
the PEAKS software. The first step is to combine the two files generated by
PEAKS.

The files coming from peaks should be generated according to the instructions 
found [here](www/PeaksDataAnalysis_howto.pdf).

@@

### Loading the files ###
lfq_filename <- "tests/testdata/protein-peptides-lfq.csv"
# file "protein-peptides.csv" exported from PEAKS identification
id_filename <- "tests/testdata/protein-peptides-id.csv"

# Prepare the data for normalyzer analysis
peaks_prepared_data <- prepare_peaks(lfq_filename, id_filename)
```

### Formating Proteome Discoverer File Outputs.

We can prepare proteome discover files for analysis with mspms as follows.

```{r}
prepared_proteome_discoverer <- prepare_pd("tests/testdata/proteome_discoverer_output.xlsx")
```

### Calculating all cleavages

We might want to calculate all possible cleavages for the peptide library 
sequences. This is useful for downstream analysis, especially when we are 
looking at the specificity of the cleavage sites via plot_cleavage_motif() as
this requires a background of all possible cleavages

We can do this by specifying the number of amino acids after the cleavage site 
that we are interested in. First lets try 4, which is the default.

```{r}
all_peptide_sequences <- mspms::calculate_all_cleavages(mspms::peptide_library$library_real_sequence,
  n_AA_after_cleavage = 4
)
head(all_peptide_sequences)
```

We could also try 5 AA after each cleavage site

```{r}
all_peptide_sequences <- mspms::calculate_all_cleavages(mspms::peptide_library$library_real_sequence,
  n_AA_after_cleavage = 5
)
head(all_peptide_sequences)
```

## Data Normalization/ Processing

### Loading design matrix

Before we normalyze data, we need to know what samples are in what groups. We can do that by defining a design matrix. 
```{r}
design_matrix <- readr::read_csv("tests/testdata/design_matrix.csv")

head(design_matrix)
```
### Normalyzing data

mspms uses the NormalyzerDE package to do normalization under the hood.

We can normalyze the data as follows:  
```{r}
normalyzed_data <- normalyze(peaks_prepared_data, design_matrix)

@@

### Handling Outliers

Here we use a Dixon test from the outliers package to detect outliers from each 
of our replicates. We need to know what samples are part of which groups, so we 
need to specify the design matrix here too. Make sure that the column header 
names are "sample" and "group" just like before.

```{r}
design_matrix <- readr::read_csv("tests/testdata/design_matrix.csv")
outliers <- handle_outliers(normalyzed_data, design_matrix)

@@

### Imputation of data

We have a lot of missing, or 0 values. For these, we need to impute them so we 
can do downstream statistics.

```{r}
imputed <- mspms::impute(outliers)

### Joining with Library

Next we need to join everything with the sequences of the peptide library.  
```{r}
joined_with_library <- mspms::join_with_library(imputed)
```

### Calcuating cleavages.

Next, we need to determine where the peptide sequences are cleaved.

We check both the N and C terminus.

Sequences are presented as the user specified number of amino acids on 
both sides of a cleavage. The default is 4, but there is interest in looking at
motifs that are farther away from the cut site. Note that X indicates that there
was nothing at that position because it is over the end.

```{r}
cleavage_added_data <- mspms::add_cleavages(joined_with_library, n_residues = 4)

head(cleavage_added_data)
```

### Adding metadata back

We need to add information about our samples back to perform downstream 
statistics on the data. We accomplish this with the prepare for stats file.

```{r}
prepared_for_stats <- mspms::prepare_for_stats(cleavage_added_data,
                                               design_matrix)
```

### Polishing

This function polishes the data by combining the cterm and nterm cleavage 
information into one column while removing any rows that don't have any 
cleavage information or have cleavage information on the cterm and nterm.

```{r}
polished_data <- mspms::polish(cleavage_added_data)
```

### Complete workflow

There are a lot of steps to get to the final normalized data we listed above. 
We have combined all of these steps into one function, mspms() for convenience.
This offers a nice balance between allowing the user the option to use 
individual steps and providing a quick way to get to the final data.

```{r}
mspms_data <- mspms::mspms(peaks_prepared_data, design_matrix)
```

mspms provides a number of convenience functions to conduct statistics
on the data.

First, we need to prepare the data for stats. This involves reshaping the data 
into the long format so it is easy to conduct statistics on and then appending 
the data in the design matrix that allows us to determine what sample contains 
what conditions/time and conduct the appropriate statistics.

Now we can conduct the statistics:

### T tests

T tests are performed within each condition and compared to time 0.

For example, for an experiment where there are two conditions, 
DMSO and MZB as well as 3 time points, 0, 1, and 2, the t tests would be
as follows:

* DMSO.TO vs DMSO.T0. 
* DMSO.T0 vs DMSO.T1. 
* DMSO.T0 vs DMSO.T2.

* MZB.T0 vs MZB.T0. 
* MZB.T0 vs MZB.T1. 
* MZB.T0 vs MZB.T2.

```{r}
# Perform T test
t_test_stats <- mspms::mspms_t_tests(mspms_data)
```

### log2FC

We can also calculate the log 2 fold change. 
The comparisons here are the same as for the T tests.  
```{r}
# calculate log2fc
log2fc <- mspms::mspms_log2fc(mspms_data)

head(log2fc)
```

### log2fc_t_tests.

Oftentimes (such as when you want to make volcano plots) it is most useful to
look at the log2fc and the t test statistics at the same time.

```{r}
log2fc_t_test <- mspms::log2fc_t_test(mspms_data)

head(log2fc_t_test)
```

### log2fct_condition

You may wish to compare two conditions at a specific time point. 
This function allows this

```{r}
condition_t = mspms::log2fct_condition(mspms_data,
                                       ref_condition = "DMSO",
                                       comparison_condition = "MZB",
                                       at_time = 60)

head(condition_t)

### log2fct_time

You may wish to compare two time points within a specific condition. 
This function allows

```{r}
time_t = mspms::log2fct_time(mspms_data,
                             within_condition = "DMSO",
                             ref_time = 0,
                             comparison_time = 60)

head(time_t)
```

### ANOVA

We also might want to perform an anova. Here, we have it set up to show the 
effect of time within each condition.

For example, for an experiment where there are two conditions, DMSO and MZB as
well as 3 time points, 0, 1, and 2, the anova would statistics for the effect of
time for each peptide within DMSO or MZB.

```{r}
# Doing ANOVA
anova_stats <- mspms::mspms_anova(mspms_data)

head(anova_stats)
```

## Common Data Visualizations

We also provide some functions that make common data visualizations easier.

### volcano plots

```{r}
volcano_plot <- mspms::plot_volcano(log2fc_t_test)

volcano_plot
```

### Plotting sequence specificity motif

Here use an approach similar to what is implemented in ICELOGO to visualize the
sequence specificity of the cleavage sites. This was used as reference to build 
the code: https://iomics.ugent.be/icelogoserver/resources/manual.pdf.

Below we can see this applied to see what cleavage sequences are enriched among
the peptides significantly different between time 0 and time 60 
within DMSO.

```{r}
cleavage_seqs <- time_t %>%
  dplyr::filter(log2fc > 3, p.adj <= 0.05) %>%
  dplyr::pull(cleavage_seq)

background_universe <- mspms::all_possible_8mers_from_228_library

mspms::plot_icelogo(cleavage_seqs, background_universe)
```

We could also look at the fold change instead of the percent difference

```{r}
mspms::plot_icelogo(cleavage_seqs, background_universe, type = "fold change")
```

We also provide a convenience function for looking at all icelogos relative to 
time 0 within the experiment.

This function includes cleavages that were significant at any time point once in 
the experimental set of the ICELOGO.

```{r}
mspms::plot_all_icelogos(mspms_data)
```

### PCA.

We can generate a PCA plot to visualize the data. 
Here, the colors show the different time points while the shape shows 
the different conditions.

```{r}
mspms::plot_pca(mspms_data)
```

### Hierchical clustering

We can also generate an interactive heatmap with the hierarchical clustering 
results.

The format of this readme does not allow for interactivity, so a static picture 
of the output is shown instead.

```{r,eval = FALSE}
mspms::plot_heatmap(mspms_data)
```

![](plot_heatmap_output.png)

### Ploting time course.

We also provide a function for plotting the mean intensity and standard 
deviation over time for each peptide in the data set by conditions.
Facets show peptide, color shows the condition.

This can be used in combination with the ANOVA function.
Below, we will use anova to calculate the peptides where we see an 
effect of time (in the DMSO group), and then plot these.

top10sig <- anova_stats %>%
  dplyr::arrange(p.adj) %>%
  dplyr::pull(Peptide) %>%
  head(10)

p1 <- mspms_data %>%
  dplyr::filter(Peptide %in% top10sig) %>%
  mspms::plot_time_course()

## Calculating the number of cleavages at each position in the library

We can also calculate the number of cleavages at each position of the library.
Here we will do this for peptides significantly different relative to time 0 for
DMSO and MZB.

```{r}
# Performing T tests
t_tests = log2fc_t_test(mspms_data) %>% 
  dplyr::filter(p.adj < 0.05,
                log2fc > 3)

count = mspms::count_cleavages_per_pos(t_tests)

p1 = mspms:::plot_cleavages_per_pos(count)

>>>>

---
output: github_document
---

@@

<!-- badges: start -->

[![R-CMD-check](https://github.com/baynec2/mspms/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/baynec2/mspms/actions/workflows/R-CMD-check.yaml)
[![Codecov test
coverage](https://codecov.io/gh/baynec2/mspms/branch/main/graph/badge.svg)](https://app.codecov.io/gh/baynec2/mspms?branch=main)
[![BioC
status](http://www.bioconductor.org/shields/build/release/bioc/mspms.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/mspms)

<!-- badges: end -->

The goal of mspms is provide a R Package that can be used to analyze data from
the [Multiplex Substrate Profiling by Mass Spectrometry (MSP-MS)
method](https://pubmed.ncbi.nlm.nih.gov/36948708/).

@@

```{r,eval = FALSE}
mspms::generate_report(
  prepared_data = mspms::peaks_prepared_data,
  colData = mspms::design_matrix,
  outdir = "../Desktop/mspms_report"
)
```

The above command will generate a .html file containing a generic mspms
analysis.

@@

Functions in this package are logically divided into 4 broad types of functions.

1.  Pre-processing data. These functions are focused on getting all of the data
    necessary for a mspms analysis together and in a consistent format.

2.  Data processing. These functions allow the user to process the proteomics
    data (imputation, normalization, etc).

@@

**Note that only a subset of functions are exported to the user.** Helper
functions can be found in the \_helper_functions.R files.

## Pre-processing data

Pre-processing data here refers to standardizing the data exported from
different software solutions for analyzing mass spectrometry-based proteomics
and adding useful information specific to the MSP-MS assay.

Specifically, the data from the file exported from the upstream software is
parsed to contain the **peptide** (detected peptide sequence, cleavages are
represented as "\_"), **library_id** (name of the peptide in the peptide library
each detected peptide maps to), and intensities for each sample.

Information about each peptide relative to the peptide it was derived from is
then added. This includes the **cleavage_seq** (the motif the peptide a user
specified n residues up and down from the cleavage event), **cleavage_pos**
(position of the peptide library the cleavage product was cleaved at ),
**peptide_type** (whether the detected peptide is a cleavage product of the
peptide library, or a full length member of the peptide library).

All of the information is then loaded as a QFeatures object along with colData
(metadata about each sample) where it is stored as a SummarizedExperiment object
named "peptides".

#### Uploading your colData

As briefly described above, the colData contains metadata describing the samples
you are trying to analyze.

It is very important that this contains at least the following columns
-"quantCols","group","condition",and "time".

The quantCols field contains the name of each sample. These names must match
whatever the samples are named in the files exported from the upstream
proteomics software.

The group field contains text specifying what group each sample belongs to. All
replicate samples should have the same group name

The condition field contains the experimental conditions that vary in your
MSP-MS experiment (this depends on the experimental question, could be type of
protease, the type of inhibitor, etc)

The time field contains the duration of incubation of your protease of interest
with the peptide library for each sample.

An example of a valid colData file is shown below.

```{r}
colData = readr::read_csv("inst/extdata/colData.csv")
usethis::use_data(colData,overwrite = TRUE)

head(colData)
```

#### PEAKS

Analysis using a .csv exported from [PEAKS
software](https://www.bioinfor.com/peaks-studio/) is supported.

an exported .csv file can be generated from PEAKS as follows:

1.  Create a New Project in PEAKS.\
2.  Select data to add to PEAKS project.\
3.  Add data, rename samples, set correct parameters. • Highlight all the added
    data.\
    • Select Create new sample for each file.\
    • Select appropriate instrument and fragmentation method.\
    • Set Enzyme to “None”.\
    • Rename samples according to enzymes, time points, and replicates.\
    • Can also ensure appropriate data is selected for these.\
    • Select “Data Refinement” to continue.\
4.  Data Refinement.\
    • On the top right, select MSP-MS as the predefined parameters.\
    • Parameters shown are what should be used for MSP-MS data analysis.\
    • Select “Identification” to continue.\
5.  Peptide Identification.\
    • On the top right, select MSP-MS as the predefined parameters.\
    • Parameters shown are what should be used for MSP-MS data analysis.\
    • Identification -\> Select Database -\> TPD_237.\
    • Identification -\> no PTMs.\
    • Can remove the PTMs by highlighting them and selecting Remove\
6.  Label Free Quantification.\
    • Make sure Label Free is selected.\
    • Group samples -\> add quadruplicates of samples to new group.

@@

# File path of peaks lfq file
lfq_filename <- "inst/extdata/peaks_protein-peptides-lfq.csv"

# Prepare the data 
peaks_prepared_data <- mspms::prepare_peaks(lfq_filename,
                                            colData,
                                            0.3,
                                            n_residues = 4)

usethis::use_data(peaks_prepared_data,overwrite = TRUE)

peaks_prepared_data
```

#### Proteome Discoverer

Analysis using a .csv file exported from [proteome
discoverer](https://www.thermofisher.com/us/en/home/industrial/mass-spectrometry/liquid-chromatography-mass-spectrometry-lc-ms/lc-ms-software/multi-omics-data-analysis/proteome-discoverer-software.html)
is supported.

To generate this .csv file:

@@

#### Fragpipe

Data exported from [Fragpipe](https://github.com/Nesvilab/FragPipe) as a .tsv
file is supported.

To generate this file, run a [LFQ Fragpipe
workflow](https://fragpipe.nesvilab.org/docs/tutorial_lfq.html) using your
desired parameters (we recommend using match between runs).

You will find a file named "combined_peptide.tsv" in the output folder from
Fragpipe.

This can be loaded into mspms as follows:

```{r}
lfq_file_path = "inst/extdata/fragpipe_combined_peptide.tsv"

fragpipe_prepared_data = prepare_fragpipe(lfq_file_path,
                                          colData)

fragpipe_prepared_data
```

## Data Processing

Data processing includes imputation and normalization of the proteomics data.

**Add more info**

```{r}
# does set seed matter?
set.seed(2)
processed_qf = process_qf(peaks_prepared_data)

usethis::use_data(processed_qf,overwrite = TRUE)

processed_qf
```

MSP-MS analysis has traditionally used T-tests to what peptides are
significantly different relative to T0. The authors of the assay suggest using a
T-test derived FDR adjusted p value threshold \<= 0.05 and log2 fold change
threshold \>= 3.

We provide a user-friendly implementation of this statistical test as follows:

```{r}
log2fc_t_test_data = mspms::log2fc_t_test(processed_qf = processed_qf)

usethis::use_data(log2fc_t_test_data,overwrite = TRUE)
```

Please note that statistical analyses are one of the strengths of the
Bioconductor project and several packages provide alternative statistical
approaches that are more flexible than t-tests and could be used with the
QFeatures objects produced by mspms.

This includes packages using empirical Bayesian approaches (see
[limma](https://bioconductor.org/packages/release/bioc/html/limma.html)) and
mixed modelling (see
[msqrob2](https://bioconductor.org/packages/release/bioc/html/msqrob2.html)),
that are suited for proteomics data.

Users are encouraged to use these excellent packages.

## Data Visualizations

We provide a number of data visualizations as part of the mspms_package.

### QC Checks

A critical initial step in MSP-MS data analysis is a rigorous quality control
assessment. Given the reliance on a specific peptide library, calculating the
percentage of library peptides detected in each sample provides a
straightforward yet powerful indicator of data integrity. Anomalously low
detection rates signal potential instrument or experimental problems.

We can see the percentage of the peptide library that were undetected among each
group of replicates as follows (for full length peptides a threshold of \~\< 10
is considered good while for cleavage products a threshold \~\< 5 is good):

```{r}
plot_qc_check(processed_qf,
              full_length_threshold = 10,
              cleavage_product_threshold = 5)
```

We can also see in what percentage of samples each peptide in the peptide
library were undetected in.

```{r}
plot_nd_peptides(processed_qf)
```

### Heatmap

We can inspect our data using an interactive heatmap as follows:

```{r}
plot_heatmap(processed_qf)
```

### PCA

We can also inspect our data using a PCA as follows.

```{r}
plot_pca(processed_qf)
```

### Volcano plots

We can generate volcano plots showing the significant peptides from each
condition as follows:

```{r}
plot_volcano(log2fc_t_test_data)
```

### Cleavage Position Plots

We can also create plots showing the number of times we observe a cleavage at
each position of the peptide_library among a set of peptides of interest.

We can do this as follows:

```{r}
sig_cleavage_data = log2fc_t_test_data %>% 
  dplyr::filter(p.adj <= 0.05,log2fc > 3)

p1 = mspms::plot_cleavages_per_pos(sig_cleavage_data )

### iceLogo

[Icelogos](https://www.nature.com/articles/nmeth1109-786) are a method for
visualizing conserved patterns in protein sequences through probability theory.

As part of the mspms R package, we have implemented the logic to generate
[iceLogos](https://genesis.ugent.be/uvpublicdata/icelogo/iceLogo.pdf) in R.

To use this, we first have to define a vector of cleavage sequences that we are
interested in. We will do this for the significant CatA cleavages below.

```{r}
catA_sig_cleavages = log2fc_t_test_data %>% 
  dplyr::filter(p.adj <= 0.05,log2fc > 3) %>% 
  dplyr::filter(condition == "CatA") %>% 
  dplyr::pull(cleavage_seq) %>% 
  unique()
```

We also need to know all of the possible cleavages we could see among our
peptide library. We can generate that as below:

```{r}
all_possible_8mers_from_228_library = calculate_all_cleavages(mspms::peptide_library$library_real_sequence,n_AA_after_cleavage = 4)

usethis::use_data(all_possible_8mers_from_228_library,overwrite = TRUE)
```

We can then generate an iceLogo relative to the background of all possible
cleavages in our peptide library like so:

```{r}
plot_icelogo(catA_sig_cleavages,
             background_universe = all_possible_8mers_from_228_library)
```

We also provide a function that conveniently plots all icelogos from all
conditions from the experiment all together.

```{r,fig.height = 10, fig.width = 4}
sig_cleavage_data = log2fc_t_test_data %>% 
  dplyr::filter(p.adj <= 0.05,log2fc > 3)

plot_all_icelogos(sig_cleavage_data)
```

### Plotting a Time Course

We can also plot the intensities of peptides of interest over time.

First we need to define which peptides we are interested in. Here we will use
the t-test results, and look at the peptide with the max log2fc.

```{r}
max_log2fc_pep = log2fc_t_test_data %>% 
  dplyr::filter(p.adj <= 0.05,log2fc > 3) %>% 
  dplyr::filter(log2fc ==max(log2fc)) %>% 
  pull(peptide)

@@

We can then filter our QFeatures object to only include this peptide

```{r}
filter = QFeatures::VariableFilter(field = "peptide",
               value = max_log2fc_pep,
               condition = "==")

sel = QFeatures::filterFeatures(processed_qf,filter)
```

And then plot as follows:

```{r}
plot_time_course(sel,summarize_by_mean = FALSE)
```
